\documentclass[10pt,a4paper]{article}

\usepackage[left=1.5cm, right=1.5cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage[svgnames]{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}

% Define colors
\definecolor{primary}{HTML}{003366}
\definecolor{secondary}{HTML}{336699}

% --- Custom Commands ---
\newcommand{\pubitem}[1]{\item #1}

\begin{document}

% Reserve space at top for logo
\vspace*{1.5cm}

% --- Name ---
\noindent\textbf{Name}

\noindent Name: Ting Dang, (H-index: 17)

\vspace{0.5em}

% --- Academic qualifications ---
\noindent\textbf{Academic qualifications}

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{@{}p{2cm}p{2cm}Xp{3cm}p{2.5cm}@{}}
\toprule
From & To & University/college attended & Subject read & Qualification \\
\midrule
08/2014 & 06/2018 & University of New South Wales (UNSW) & Signal Processing \& Machine Learning & PhD \\
09/2012 & 03/2015 & Northwestern Polytechnical University & Signal Processing & M.Eng. \\
09/2008 & 03/2012 & Northwestern Polytechnical University & Signal Processing & B.Eng. \\
\bottomrule
\end{tabularx}
\end{table}

\vspace{0.5em}

% --- Previous academic positions ---
\noindent\textbf{Previous academic positions}

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{@{}p{2cm}p{2cm}X@{}}
\toprule
From & To & Organisation and position held \\
\midrule
10/2022 & 12/2023 & Senior Research Scientist, Nokia Bell Labs, UK \\
01/2021 & 10/2022 & Senior Research Associate, University of Cambridge, UK \\
05/2018 & 12/2020 & Research Associate, University of New South Wales (UNSW), Australia \\
\bottomrule
\end{tabularx}
\end{table}

\vspace{0.5em}

% --- Present academic position ---
\noindent\textbf{Present academic position}

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{@{}p{2cm}p{2cm}X@{}}
\toprule
From & To & Organisation and position held \\
\midrule
03/2024 & Now & Senior Lecturer, University of Melbourne, Australia \\
\bottomrule
\end{tabularx}
\end{table}

\vspace{0.5em}

% --- Selected Professional Memberships ---
\noindent\textbf{Selected Professional Memberships}

{\small
\noindent\begin{tabularx}{\textwidth}{@{}p{3.2cm}X@{}}
\toprule
Date & Organisation and position held \\
\midrule
2016--present & Member, IEEE \\
2021--present & Member, ACM \\
2025--present & Editor, \textit{Computer Speech and Language} \\
2024--present & Editor, \textit{IEEE Pervasive Computing} \\
2023--present & Senior Program Committee Member, AAAI \\
2025--present & Area Chair, ICASSP \\
\bottomrule
\end{tabularx}
}

\vspace{0.5em}

% --- Previous relevant research work (Funding History) ---
\noindent\textbf{Previous relevant research work (Funding History)}

\begin{enumerate}[leftmargin=*, label=\arabic*.]
    \item Benchmarking Auditory Cognitive Reasoning in Audio-Language Models, (Amount: \$85,000)
    
    Funder: Google Research Fund.
    
    Role: Lead PI \hfill 2026
    
    \item AI Centre for the Empowerment of Human Learning, (Amount: \$300,000)
    
    Funder: Norway National Centre for AI and Learning, \hfill 2026 -- 2028
    
    Role: Co-PI.
    
    \item Multi-site Human Study on Non-invasive Alcohol Detection using Smart Wearable Technology, (Amount: \$36,000)
    
    Funder: WHG Fund \hfill 2025 -- 2026
    
    Role: Co-PI.
    
    \item Emotional Speech Generation for Intelligent Dialogue Systems, (Amount: ¥50,000)
    
    Funder: Wuhan University Collaborative Seed Grant \hfill 2025 - 2026
    
    Role: Lead PI.
    
    \item Multimodal LLMs for Mobile Health, (Amount: \$16,000)
    
    Funder: OpenAI Researcher Access Grant \hfill 2024
    
    Role: Lead PI.

    \item EAR: Audio-based Mobile Health Diagnostics, (Amount: €2.5M)
    
    Funder: European Research Council \hfill 2019 -- 2025

    Role: Participant.

    \item Integrating biologically-inspired auditory models into deep learning, (Amount: \$385,000)
    
    Funder: Australian Research Council \hfill 2019 -- 2021

    Role: Participant.
\end{enumerate}

\vspace{0.5em}

% --- Publications Section A ---
\noindent\textbf{Publications (Section A - Five most representative publications in recent five years)}

\begin{enumerate}[leftmargin=*, label=\arabic*.]
    \pubitem{Dong, J., Jia, H., Chatterjee, S., Ghosh, A., Bailey, J., \textbf{Dang, T. (Corresponding Author)} (2025). E-BATS: Efficient Backpropagation-Free Test-Time Adaptation for Speech Foundation Models. In \textit{Advances in Neural Information Processing Systems} (NeurIPS), 2025.}

    \pubitem{Halim, J., Wang, S., Jia, H., \textbf{Dang, T. (Corresponding Author)} Token-Level Logits Matter: A Closer Look at Speech Foundation Models for Ambiguous Emotion Recognition. In \textit{INTERSPEECH}, 2025.}
    
    \pubitem{\textbf{Dang, T. (First Author)}, Han, J.\textsuperscript{*}, Xia, T.\textsuperscript{*}, Bondareva, E., Brown, C., Chauhan, J., Grammenos, A., Spathis, D., Cicuta, P., Mascolo, C. (2023). Conditional Neural ODE Processes for Individual Disease Progression Forecasting: A Case Study on COVID-19. In \textit{Proceedings of the ACM SIGKDD Conference on Knowledge Discovery and Data Mining} (KDD), 2023.}
    
    \pubitem{\textbf{Dang, T. (First Author)}, Spathis, D., Ghosh, A., Mascolo, C. (2023). Human-centered AI for mobile health sensing: challenges and opportunities. \textit{Royal Society Open Science}. \textbf{[Featured in Special Collection]}}
    
    \pubitem{\textbf{Dang, T. (First Author)}, Han, J.\textsuperscript{*}, Xia, T.\textsuperscript{*}, Spathis, D., Bondareva, E., Brown, C., Chauhan, J., Grammenos, A., Hasthanasombat, A., Floto, A., Cicuta, P., Mascolo, C. (2022). Exploring Longitudinal Cough, Breath, and Voice Data for COVID-19 Disease Progression Prediction via Sequential Deep Learning. \textit{Journal of Medical Internet Research}. \textbf{[Media Coverage]}}
\end{enumerate}

\vspace{0.5em}

% --- Publications Section B ---
\noindent\textbf{Publications (Section B - Five representative publications beyond the recent five-year period)}

\begin{enumerate}[leftmargin=*, label=\arabic*.]
    \pubitem{\textbf{Dang, T. (First Author)}, Sethu, V., Ambikairajah, E. (2018). Compensation Techniques for Speaker Variability in Continuous Emotion Prediction. \textit{IEEE Transactions on Affective Computing}.}
    
    \pubitem{\textbf{Dang, T. (First Author)}, Sethu, V., Ambikairajah, E. (2018). Dynamic Multi-rater Gaussian Mixture Regression Incorporating Temporal Dependencies of Emotion Uncertainty Using Kalman Filters. In \textit{Proceedings of the IEEE International Conference on Acoustics, Speech and Signal Processing} (ICASSP), 2018.}
    
    \pubitem{\textbf{Dang, T. (First Author)}, Sethu, V., Epps, J., Ambikairajah, E. (2017). An Investigation of Emotion Prediction Uncertainty Using Gaussian Mixture Regression. In \textit{Proceedings of the Annual Conference of the International Speech Communication Association} (INTERSPEECH), 2017.}

    \pubitem{\textbf{Dang, T. (First Author)}, Stasak, B., Huang, Z., Jayawardena, S., Atcheson, M., Hayat, M., Le, P., Sethu, V., Goecke, R., Epps, J. (2017). Investigating Word Affect Features and Fusion of Probabilistic Predictions Incorporating Uncertainty in AVEC 2017. Proceedings of the 7th International Workshop on Audio/Visual Emotion Challenge, in conjunction with ACM MM, 2017}
    
    \pubitem{\textbf{Dang, T. (First Author)}, Sethu, V., Ambikairajah, E. (2016). Factor Analysis Based Speaker Normalisation for Continuous Emotion Prediction. In \textit{Proceedings of the Annual Conference of the International Speech Communication Association} (INTERSPEECH), 2016.}
\end{enumerate}

\end{document}

